Races with hyper3 objects

### 2022-07-28 inst/race3.Rmd
more cool work

o <- function(h){maxp(allvenues(h),give=TRUE,n=1)$likes}
l <- seq(from=0.9,to=4,len=11)
L <- sapply(l,o)
```

@@

```{r,label=maxwithfour,cache=TRUE}
o <- maxp(allvenues(4),give=TRUE,n=1,hessian=TRUE)
```

```{r,analyse4}
pie(o$par)
eigen(o$hessian)$values
```

>>>>

o <- function(h){maxp(allvenues(h),give=TRUE,n=1)$likes}
l <- seq(from=0.9,to=2.5,len=11)
L <- sapply(l,o)
```

@@

```{r,findmaxlikeusingoptim,cache=TRUE}
jj <- optimize(o,c(1.3,1.5),maximum=TRUE)
jj
```

```{r,likelihoodnull,cache=TRUE}
(jjnull <- o(1))
```

```{r}
pchisq(2*(jj$objective-jjnull),df=1,lower.tail=FALSE)
```

```{r,label=maxwithfour,cache=TRUE}
mv_max  <- maxp(allvenues(jj$maximum),give=TRUE,n=1)
mv_null <- maxp(allvenues(1),give=TRUE,n=1)
```

```{r,analyse4}
x <- mv_max$par
y <- mv_null$par
par(pty='s')
plot(x,y,asp=1,pch=16,xlim=c(0,0.2),ylim=c(0,0.2),xlab="null",ylab="max like")
for(i in seq_along(x)){text(x[i],y[i],names(x)[i],pos=4,cex=0.7,col='gray')}
abline(0,1)
```
